Video-Agnostic Perturbations: Efficient Targeted Attacks for Siamese Visual Tracking

### 2021-04-19 博士/论文提交/adversarial_attack/TCSVT/latex/bare_jrnl.tex
扩至9页

>>>>

\begin{figure*}[t!]
  \begin{center}
    \includegraphics[width=0.3\textwidth]{images/OTB2015/success_plot_OPE_OTB100_BC.png}
    \includegraphics[width=0.3\textwidth]{images/OTB2015/success_plot_OPE_OTB100_DEF.png}
    \includegraphics[width=0.3\textwidth]{images/OTB2015/success_plot_OPE_OTB100_FM.png}
    \includegraphics[width=0.3\textwidth]{images/OTB2015/success_plot_OPE_OTB100_IPR.png}
    \includegraphics[width=0.3\textwidth]{images/OTB2015/success_plot_OPE_OTB100_IV.png}
    \includegraphics[width=0.3\textwidth]{images/OTB2015/success_plot_OPE_OTB100_LR.png}
    \includegraphics[width=0.3\textwidth]{images/OTB2015/success_plot_OPE_OTB100_MB.png}
    \includegraphics[width=0.3\textwidth]{images/OTB2015/success_plot_OPE_OTB100_OCC.png}
    \includegraphics[width=0.3\textwidth]{images/OTB2015/success_plot_OPE_OTB100_OPR.png}
    \includegraphics[width=0.3\textwidth]{images/OTB2015/success_plot_OPE_OTB100_OV.png}
    \includegraphics[width=0.3\textwidth]{images/OTB2015/success_plot_OPE_OTB100_SV.png}
  \end{center}
     \caption{FDSA}
  \label{fig:globally_uav20l_1}
\end{figure*}
